---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# semicoloner

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of semicoloner is format code according to one rule: Put a semi-colon
after every expression. It is an example for a custom [{styler}](https://styler.r-lib.org)
style guide.

## Installation

You can install the released version of semicoloner from [CRAN](https://CRAN.R-project.org) with:

``` r
remotes::install_github("lorenzwalthert/semicoloner")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(semicoloner)
cache_deactivate()
text <- 'communicate_warning <- function(changed, transformers) {
  if (any(changed, na.rm = TRUE) &&
    !can_verify_roundtrip(transformers) &&
    !getOption("styler.quiet", FALSE)
  ) {
    cat("Please review the changes carefully!", fill = TRUE)
  }
}
a
b
c /
  3
d + 3
'

style_text(text)
```


## Principles 

* re-export all exported functions from {styler}, `purrr::partial()` style guide
  arguments with third-party style guide.
